

%-----------OUTREACH-----------------%
\section{\textbf{Outreach}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Student Peer Mentor } % Position
    {UM School of Information} %Club,Event
    {Aug. 2022- Dec. 2022} %Tenure Period
        \vspace{-2mm}



\resumePOR{Teaching Assistant } % Position
    {Intro to Theatre} %Club,Event
    {May 2021- Aug. 2021} %Tenure Period
        \vspace{-2mm}
\resumePOR{Teaching Assistant } % Position
    {Academic Writing I \& II} %Club,Event
    {Sept. 2020 - Apr. 2021} %Tenure Period
        \vspace{-2mm}

\resumePOR{Core Member } % Position
    {SJTU Network and Information Management Organization}%Club,Event
    {Oct. 2019 - June 2021} %Tenure Period
        \vspace{-2mm}  

\resumePOR{Core Member } % Position
    {SJTU Photography Association} %Club,Event
    {Oct. 2020 - Aug. 2021} %Tenure Period
        \vspace{-2mm}  

\resumePOR{Vice Director } % Position
    {UM-SJTU Joint Institute Student Union Tech Department} %Club,Event
    {Oct. 2019 - June 2020} %Tenure Period
        \vspace{-2mm}  
        
\resumeSubHeadingListEnd
\vspace{-5mm}


%----------------Honors and Awards------------------%
\section{\textbf{Honors, Awards \& Grants}}
\vspace{-0.4mm}
\resumeSubHeadingListStart 

\resumePOR{} % Position
    {UM-SJTU Joint Institute Student Development Scholarship} %Club,Event
    {Apr. 2021} %Tenure Period
        \vspace{-2mm}
\resumePOR{} % Position
    {The Mathematical Contest in Modeling (MCM) Successful Participant} %Club,Event
    {Feb. 2021} %Tenure Period
        \vspace{-2mm}
\resumePOR{} % Position
{SJTU Innovative and Pioneering Project (IPP) Grant (\textyen 8000)} %Club,Event
    {Oct. 2020} %Tenure Period
        \vspace{-2mm}
% \resumePOR{} % Position
% {SJTU Outstanding Individual in Summer Social Practice} %Club,Event
%     {Oct. 2019} %Tenure Period
        % \vspace{-2mm}

\resumeSubHeadingListEnd
\vspace{-5mm}
%-----------Technical skills-----------------
\section{\textbf{Skills}}
\vspace{1mm}
 \begin{itemize}[leftmargin=0.05in, label={}]
\item \textbf{Programming: }{Python, C++, Markdown, LaTex, JavaScript, CSS, HTML, SQL, R, Matlab, Shell, Verilog} \\
\textbf{Framework/Toolkits: }{React, Django, Hadoop, Android Studio; Raspberry Pi, Arduino}\\
\textbf{Software: }Figma, Adobe Creative Cloud (XD, Illustrator, Photoshop), Miro, Unity, Unreal Engine\\
\textbf{Language: }Chinese (Native), English (Professional, TOEFL 108), Spanish and Japanese (Beginner)\\
\textbf{Coursework: }Probability and Statistics, Methods and Tools for Big Data, Needs Assessment and Usability Evaluation, Online Communities, Accessibility, Applied Machine Learning, Sociology, Linguistics

      % \resumeItemListStart
      % \item{Coursework: Intro to Sociology(A), Intro to Linguistics(A)}
      % \resumeItemListEnd

      %     \resumeItemListStart
      %       \vspace{-2.0mm}
      % \item{Coursework: AI Interaction Technologies, Probability and Statistics, Data Structure and Algorithms, Methods and Tools for Big Data, Networks, Introduction to Computer Organization, Signals and Systems}
      % \item{Electives for Industrial Design: Ergonomics, Product Design, Interaction Design}
      % \resumeItemListEnd


    
 \end{itemize}
 \vspace{-16pt}